dyngen: benchmarking with \textit{in silico} single cells

### 2019-10-16 content.tex
~

By simulating a cell over time in terms of its molecular state and the reactions that are allowed to occur, the simulator is more extendible to new modalities or experimental procedures (Figure~\ref{fig:showcase}B). We demonstrate \texttt{dyngen}'s flexibility by simulating three different types of biological experiments, and using these simulations to develop benchmarking methodologies for recently developed computational tools.

>>>>

By simulating a cell over time in terms of its molecular state and the reactions that are allowed to occur, the simulator is more extendible to new modalities or experimental procedures (Figure~\ref{fig:showcase}B). We demonstrate \texttt{dyngen}'s flexibility by simulating snapshot, time-series and pertubation experiments, allowing to benchmark a wide variety of computational tools such as trajectory alignment and differential network inference methods.
